%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Postdoctoral Researcher} % Job title
    {University of Iowa} % Organization
    {Iowa City, IA} % Location
    {Jun 2017 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research on generic programming and zero-cost reuse in Curry-style dependent type theory.}
        \item {Contributed to the development of the dependently typed Cedille language.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {Portland State University} % Organization
    {Portland, OR} % Location
    {Aug 2012 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Generic dependently typed programming over type theoretic models using Agda.}
        \item {Formal correctness proofs of programming languages (especially semantic termination) using Agda.}
        \item {Implementation of dependently typed languages (Ditto and Spire) using Haskell.}
        \item {Co-authored and awarded NSF/CISE/CCF grant \#1320934.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Engine Yard} % Organization
    {San Francisco, CA} % Location
    {May 2009 - Aug 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a cloud hosting platform on top of Amazon Web Services (AWS).}
        \item {Ruby web application and API programming using Ruby on Rails and Sinatra.}
        \item {Ruby system automation using Chef.}
        \item {Unit testing using RSpec.}
        \item {Integration testing using Cucumber and Selenium.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {IZEA} % Organization
    {Orlando, FL} % Location
    {Jan 2007 - Aug 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a social media advertising platform.}
        \item {Ruby web application and API programming using Ruby on Rails.}
        \item {Unit testing using RSpec.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Bear Den Designs} % Organization
    {Jacksonville, FL} % Location
    {May 2006 - Jan 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on medical resident management software.}
        \item {Ruby web application programming using Ruby on Rails.}
        \item {Unit testing using Test::Unit.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
