%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Software}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Dependently Typed Programming Language} % Affiliation/role
    {\href{https://github.com/ditto/ditto}{Ditto}} % Organization/group
    {Haskell} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Open universe of types.}
        \item {Dependent pattern matching.}
        \item {Implicit arguments via dynamic pattern unification and constraint postponement.}
        \item {Mutual functions, induction-recursion, and induction-induction.}
        \item {Eta-equality for functions.}
        \item {Interactive holes and case splitting.}
        \item {Novel enhanced form of coverage checking.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dependently Typed Programming Language} % Affiliation/role
    {\href{https://github.com/spire/spire}{Spire}} % Organization/group
    {Haskell} % Location
    {2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Proof of concept.}
        \item {Closed universe of types.}
        \item {Generic constructors and eliminators.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Formal Web Framework} % Affiliation/role
    {\href{https://github.com/larrytheliquid/lemmachine}{Lemmachine}} % Organization/group
    {Agda} % Location
    {2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Proof of concept.}
        \item {Request headers correct w.r.t. previous headers.}
        \item {Response headers and code correct w.r.t. previous
          request and headers.}
        \item {Verified HTTP parser.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Dataflow Concurrency Library} % Affiliation/role
    {\href{https://github.com/larrytheliquid/dataflow}{Dataflow}} % Organization/group
    {Ruby} % Location
    {2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Dataflow concurrency for Ruby inspired by the Oz
          programming language.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
